Nested sampling with two objective functions

### 2016-02-09 Paper/ms.tex
Rob's words
Fixed LJ subscript
entropy prior talk

@@

@@

>>>>

In terms of the Lennard Jones parameters $\epsilon$ and $\sigma$, the
``polymer'' potential is
\begin{eqnarray}
U_{\rm polymer} &=&
\sum_{i=1}^{n-1} \phi^{(1)}_{i,i+1} + \sum_{i=2}^{n-1} \phi^{(2)}_{i-1, i, i+1}
\end{eqnarray}
where

\begin{eqnarray}
\phi^{(1)}_{i,i+1} &=& \frac{k}{2}\left(|\boldsymbol{r}_i - \boldsymbol{r}_{i+1}|- 2^{1/6}\sigma\right)^2,\\
\phi^{(2)}_{i-1, i, i+1} &=& \frac{k}{2}
\left((\boldsymbol{r}_i - \boldsymbol{r}_{i-1})\cdot(\boldsymbol{r}_{i-1} - \boldsymbol{r}_{i}) - 1\right)^2,
\end{eqnarray}
and $k=\frac{36 \times 2^{2/3}\epsilon}{\sigma^2}$ has been chosen to match
the curvature of $U_{\rm LJ}(\boldsymbol{r}_i, \boldsymbol{r}_j)$.

@@

The prior for the pixel intensities $\{m_i\}$ has an ``entropic'' form,
where images are upweighted (relative to a uniform prior) if the pixel
intensities have a low dynamic range. The prior density is
\begin{eqnarray}
p(\boldsymbol{m}) \propto \exp
\left[
-\lambda \sum_{i=1}^n m_i \ln m_i
\right]
\end{eqnarray}
where $\lambda$ is a hyperparameter.

In the 1980s, this prior was thought to have a fundamental status, but this
is no longer the case \citep{massinf}. Instead, we can consider the configurational
entropy $-\sum_{i=1}^n m_i \ln m_i$ as simply a function of an image that may
be relevant somehow, and that we are uncertain about.

@@

\bibitem[\protect\citeauthoryear{Skilling}{1998}]{massinf}
Skilling J., 1998, Massive Inference and Maximum Entropy, in Maximum Entropy
and Bayesian Methods, Kluwer Academic Publishers, Dordrecht/Boston/London p.14
